---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  eval = FALSE
)
```

# krpoltext

<!-- badges: start -->
[![R-CMD-check](https://github.com/taehyun-lim/krpoltext/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/taehyun-lim/krpoltext/actions/workflows/R-CMD-check.yaml)
[![License: MIT](https://img.shields.io/badge/code-MIT-blue.svg)](https://opensource.org/licenses/MIT)
[![License: CC BY-NC-ND 4.0](https://img.shields.io/badge/data-CC%20BY--NC--ND%204.0-lightgrey.svg)](https://creativecommons.org/licenses/by-nc-nd/4.0/)
[![DOI](https://img.shields.io/badge/DOI-10.1038%2Fs41597--025--05220--4-blue)](https://doi.org/10.1038/s41597-025-05220-4)
[![DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.18704319.svg)](https://doi.org/10.5281/zenodo.18704319)
<!-- badges: end -->

**krpoltext** provides convenient R access to two large-scale Korean political
text corpora described in:

> Lim, T.H. (2025). South Korean Election Campaign Booklet and Party
> Statements Corpora. *Scientific Data*, 12, 1030.
> <https://doi.org/10.1038/s41597-025-05220-4>

| Corpus | Period | Candidates / Entries | Description |
|--------|--------|---------------------|-------------|
| **Election Campaign Booklets** | 2000–2022 | 49,678 candidates | Manifesto booklets from candidates in presidential, National Assembly, and local elections |
| **Party Statements** | 2003–2022 | 82,723 statements | Official statements and leadership meeting minutes from the two major parties |

Data is hosted on the [Open Science Framework](https://osf.io/rct9y/)
(DOI: [10.17605/OSF.IO/RCT9Y](https://doi.org/10.17605/OSF.IO/RCT9Y)) and
**automatically downloaded** on first use.

## Installation

```{r install}
# install.packages("remotes")
remotes::install_github("taehyun-lim/krpoltext")
```

## Quick Start

```{r quickstart}
library(krpoltext)

# Load a dataset (auto-downloads from OSF on first use, then cached)
ps <- load_party_statements()
cb <- load_campaign_booklet()

# Explore metadata
metadata("party_statements")

# Filter documents
docs_2020 <- get_docs("party_statements", year = 2020)
conservative <- get_docs("party_statements", year = 2018:2022, conservative = 1)

# Campaign booklets: filter by office and party
assembly <- get_docs("campaign_booklet", office = "national_assembly", .data = cb)
```

## Data Download

The CSV files (~1.5 GB total) are downloaded from OSF on first load:

```{r download}
# Auto-download: asks for consent interactively
ps <- load_party_statements()

# Or download all datasets at once
download_data()

# Provide a local file path instead
ps <- load_party_statements(path = "~/Downloads/sk_party_statements_v2022.csv")
```

Data is cached as compressed RDS in `tools::R_user_dir("krpoltext", "cache")`
and verified via SHA-256 checksums. Subsequent loads take ~2 seconds.

## Integration with quanteda

```{r quanteda}
library(quanteda)

corp <- as_quanteda_corpus(ps, docid_field = "id")
toks <- tokens(corp, remove_punct = TRUE)
dfm_obj <- dfm(toks)
topfeatures(dfm_obj, 20)
```

## Functions

| Function | Description |
|----------|-------------|
| `load_campaign_booklet()` | Load the campaign booklet corpus |
| `load_party_statements()` | Load the party statements corpus |
| `metadata()` | Dataset metadata (columns, counts, citation) |
| `get_docs()` | Filter documents by any column |
| `as_quanteda_corpus()` | Convert to a quanteda corpus object |
| `download_data()` | Download datasets from OSF |
| `clear_cache()` | Remove cached data files |

## Static Data API

Dataset metadata and download links are available as a static JSON API via
GitHub Pages — no server needed:

| Endpoint | Description |
|----------|-------------|
| [`/data/index.json`](https://taehyun-lim.github.io/krpoltext/data/index.json) | Resource index (files, versions, SHA-256, download URLs) |
| [`/data/metadata.json`](https://taehyun-lim.github.io/krpoltext/data/metadata.json) | Dataset descriptions and citation info |
| [`/data/schema/campaign_booklet.json`](https://taehyun-lim.github.io/krpoltext/data/schema/campaign_booklet.json) | Column schema for campaign booklets |
| [`/data/schema/party_statements.json`](https://taehyun-lim.github.io/krpoltext/data/schema/party_statements.json) | Column schema for party statements |

**R** (without installing the package):

```{r static-api-r}
api <- "https://taehyun-lim.github.io/krpoltext/data/index.json"
idx <- jsonlite::fromJSON(api)
url <- idx$resources$download_url[idx$resources$name == "party_statements"]
tmp <- tempfile(fileext = ".csv")
download.file(url, tmp, mode = "wb")
dt <- data.table::fread(tmp, encoding = "UTF-8")
```

**Python**:

```{python static-api-py, eval = FALSE}
import requests, pandas as pd
idx = requests.get("https://taehyun-lim.github.io/krpoltext/data/index.json").json()
url = next(r["download_url"] for r in idx["resources"] if r["name"] == "party_statements")
df = pd.read_csv(url)
```

Full documentation: <https://taehyun-lim.github.io/krpoltext/>

## Citation

If you use this data in academic work, please cite the Data Descriptor paper:

> Lim, T.H. (2025). South Korean Election Campaign Booklet and Party
> Statements Corpora. *Scientific Data*, 12, 1030.
> <https://doi.org/10.1038/s41597-025-05220-4>

And the data repository:

> Lim, T.H. (2024). South Korean Election Campaign Booklet Corpus and
> Party Statements Corpus. OSF.
> <https://doi.org/10.17605/OSF.IO/RCT9Y>

```{r citation}
citation("krpoltext")
```

## License

- **Package code**: [MIT License](LICENSE.md)
- **Data**: [CC BY-NC-ND 4.0](LICENSE-DATA.md) — see the [OSF project](https://osf.io/rct9y/) and the [Data Descriptor](https://doi.org/10.1038/s41597-025-05220-4) for full terms.

## Links

- Data Descriptor: <https://doi.org/10.1038/s41597-025-05220-4>
- OSF Repository: <https://osf.io/rct9y/>
- Zenodo Archive: <https://doi.org/10.5281/zenodo.18704319>
- GitHub: <https://github.com/taehyun-lim/krpoltext>
- Issues: <https://github.com/taehyun-lim/krpoltext/issues>
