---
title: "Quick Start: 5-Minute Guide to krpoltext"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Quick Start: 5-Minute Guide to krpoltext}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval = FALSE
)
```

The **krpoltext** package provides access to two Korean political text corpora
described in:

> Lim, T.H. (2025). South Korean Election Campaign Booklet and Party
> Statements Corpora. *Scientific Data*, 12, 1030.
> <https://doi.org/10.1038/s41597-025-05220-4>

## Installation

```{r install}
# install.packages("remotes")
remotes::install_github("taehyun-lim/krpoltext")
```

## Load a Dataset

If a managed artifact is needed, it is downloaded from
[OSF](https://osf.io/rct9y/) on first use in an interactive session and then
cached locally as RDS. In non-interactive sessions, use a local file path or a
pre-populated cache. The `load_*()` helpers prefer managed Parquet artifacts by
default; the examples below make that explicit. `campaign_booklet` is
available in two public variants: `original` and `enriched`. The default is
`original`; use `variant = "enriched"` when you need NEC linkage fields such
as `huboid`, `sg_id`, `sg_typecode`, and `link_status`.

```{r load}
library(krpoltext)

# Load the party statements corpus from managed Parquet
ps <- load_party_statements(format = "parquet")
ps
```

## Explore Metadata

```{r metadata}
meta <- metadata("party_statements")
meta$name
meta$time_coverage
meta$n_candidates_or_entries
meta$columns
```

## Filter Documents

`get_docs()` dynamically filters on any column that exists in the dataset.

```{r filter}
# Statements from 2020
docs_2020 <- get_docs("party_statements", year = 2020, .data = ps)
nrow(docs_2020)

# Conservative party statements from 2018-2022
conservative_recent <- get_docs(
  "party_statements",
  year = 2018:2022,
  conservative = 1,
  .data = ps
)
nrow(conservative_recent)
```

## Quick Summary

```{r summary}
table(ps$year)
table(ps$partisan)
```

## Campaign Booklets

```{r booklet}
cb <- load_campaign_booklet(format = "parquet")

# Load the NEC-linked enriched variant when needed
cb_enriched <- load_campaign_booklet(format = "parquet", variant = "enriched")
cb_enriched[, c("code", "huboid", "sg_id", "sg_typecode", "link_status")]

# National Assembly candidates only
assembly <- get_docs("campaign_booklet", office = "national_assembly", .data = cb)
nrow(assembly)

# Filter by party
table(assembly$party_eng)
```

## Next Steps

- See `vignette("replication-pipeline")` for a full text analysis workflow
  with **quanteda**.
- See the
  [Data Descriptor](https://doi.org/10.1038/s41597-025-05220-4) for variable
  definitions, technical validation, and example use cases.
